An assessment of statistical guidance for authors at influential academic journals across scientific disciplines: Preliminary analysis

### 2021-08-18 analysis/preliminaryAnalysis.Rmd
added some guidance examples

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = T)
```

@@

```{r set_style_defaults}
theme_gtsummary_compact() # set table theme
ggthemr('fresh') # set ggplot theme
```

@@

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = T, fig.topcaption = TRUE)
```

@@

```{r set_defaults}
theme_gtsummary_compact() # set table theme
ggthemr('fresh') # set ggplot theme
```

@@

```{r guidance_examples}
# get the names of the twenty statistical topics
topic_names <- d_all %>% 
  select(starts_with("has_"), -c(has_guidance, has_external_guidance, has_internal_guidance, has_internal_guidance_section, has_publisher_guidance)) %>% 
  rename_all(~str_replace(.,"^has_","")) %>% # remove has_ prefix
  verify(ncol(.) == 20) %>% # check there are twenty columns (topics) as expected
  colnames()

set.seed(42)
guidance_examples_tbl <- d_all %>%
  select(journal, topic_names) %>% 
  verify(ncol(.) == 21) %>% # check there are 21 columns as expected (i.e., journal and twenty topics)
  pivot_longer(cols = !journal, names_to = 'topic', values_to = 'verbatim') %>%
  distinct(verbatim, .keep_all = T) %>%
  drop_na(verbatim) %>%
  filter(nchar(verbatim) < 800) %>% # select shorter guidance only
  group_by(topic) %>%
  sample_n(2) %>%
  ungroup() %>%
  mutate(verbatim = paste0(verbatim,' (',journal,')')) %>% # add journal name to verbatim column
  select(-journal) %>% # remove journal column
  mutate(topic_display = case_when( # create display versions of topic names
    topic == "p_value" ~ "p values",
    topic == "significance" ~ "statistical significance",
    topic == "null_hypo" ~ "null hypotheses",
    topic == "sample_size" ~ "sample size justification",
    topic == "conf_int" ~ "confidence intervals",
    topic == "effect_size" ~ "effect sizes",
    topic == "multi_compare" ~ "multiple comparisons",
    topic == "subgroup" ~ "subgroup analyses",
    topic == "baseline_covar" ~ "baseline covariates",
    topic == "non_param" ~ "non-parametric tests",
    topic == "sensitivity" ~ "sensitivity analyses",
    topic == "model_assume" ~ "checking model assumptions",
    topic == "exclusion" ~ "data exclusions",
    topic == "outliers" ~ "handling outliers",
    topic == "missing" ~ "handling missing data",
    topic == "one_sided" ~ "one-sided tests",
    topic == "bayes" ~ "Bayesian statistics",
    topic == "secondary" ~ "secondary outcomes",
    topic == "prespecify" ~ "prespecification of analyses",
    topic == "cat_continuous" ~ "categorisation of continuous data"
  )) %>%
  select(topic = topic_display,"example guidance" =verbatim)
```

To give you a flavour of the kind of guidance provided, I have randomly selected two examples (excluding a few very long examples), for each of the twenty statistical topics, and displayed them in Table \@ref(fig:guidanceexamples) below.

```{r guidanceexamples}
guidance_examples_tbl %>% kable()
```

@@

```{r phase_two}
# export data for phase two
d_all %>% filter(has_p_value == T | has_significance == T) %>% 
  mutate(coder = "TEH") %>% 
  select(journal, esi_field, p_value, significance) %>%
  mutate(recommended_required = NA,
         p_how = NA,
         p_threshold = NA,
         stat_sig_ok = NA,
         stat_sig_alpha = NA) %>%
  write_csv(here('data','raw','templates','phase_two_pval.csv'))

```
